On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-04-22 engineering.tex
minor changes -- functional block

As depicted in Figure~\ref{fig:atom}, so far, we have considered Information
generated by a Port $P_I$ and then sent through a channel $C$ to another
(recipient) port $P_O$. In this scenario where Ports and then Channels are
atomic (otherwise raising infinite regress), we can only  consider the
relations between Ports and Channel; considering both input-port to channel and
channel to output-port. In fact, the Weaknesses of a channel are defined in terms
of the Weaknesses of Ports. Our intention is to introduce now the concept of
functional architecture and functional blocks composing the functional architecture.
Io order to define a functional block without encountering an infinite definition,
we must reach the same conclusions as for the Channel. Therefore, describing
the information as flowing over a channel or in a functional block is purely
syntactic sugar.

@@

\subsubsection{Functional Block}
A Functional Architecture, as already described beforehand, takes Information as input-Beliefs
and transforms the Information into output-Beliefs. Those transformations 
occurs within the Functional Architecture, where Functional Blocks transforms Beliefs into 
other Beliefs. Similarly to channels, we could consider a Functional Block as a Functional Architecture
occurring in an infinite regress. Therefore, we consider Functional Blocks as 
correctly executing their abstract behavior, correctly transforming inputs into outputs (Beliefs).

\begin{definition}{\bf Functional Block and Architecture --}\label{def:funblock}
	A functional block of an agent $a$ 
	takes a region of input-Beliefs and outputs a region of output-Beliefs. 
	A functional architecture is an interconnected system of functional blocks.
\end{definition}
The quality of a functional block or architecture can be expressed as a
relation between input and output belief, similarly to the quality of a channel
but inverting the flow (input$\rightarrow$output instead of
output$\rightarrow$input). In other words, we consider two properties:
how inputs are interpreted, and how outputs are produced.
One may, of course, argue that since there is a
transformation process in the functional block the quality of that
transformation process is what the theory should consider. This can
be argued not just for functional blocks (Behaviors) but also for Channels
(Assertions). As we detail afterwards, the relations considered so
far revolves around the concept of integrity or availability, while the reminder of this section 
will be focused on a broader analysis of security properties and requirements
which will also consider other security properties such as availability and
confidentiality.  In order to define the quality of the internals of a functional block or channel, we first
need to relate the concept of Facts to engineering requirements.

>>>>

As depicted in Figure~\ref{fig:atom}, so far, we have considered Information
generated by a Port $P_I$ and then sent through a channel $C$ to another
(recipient) port $P_O$. In this scenario where Ports and then Channels are
atomic (otherwise raising infinite regress), we can only  consider the
relations between Ports and Channel; considering both input-port to channel and
channel to output-port. In fact, the Weaknesses of a channel are defined in terms
of the Weaknesses of Ports. We now introduce the concept of
functional architecture and its decomposition into functional blocks. 
Io order to define a functional block without encountering a infinitely recursive definition,
we must reach the same conclusions as for the Channel. Therefore, describing
the information as flowing over a channel or in a functional block is purely
syntactic sugar.

@@

\subsubsection{Functional Block}
A Functional Architecture, as already described beforehand, takes Information as input-Beliefs
and transforms the Information into output-Beliefs. Those transformations 
occurs within the Functional Architecture, where Functional Blocks transforms Beliefs into 
other Beliefs. Similarly to channels, we could consider a Functional Block as a Functional Architecture
occurring in an infinite regress. Therefore, we consider Functional Blocks as 
executing an abstract undefined behavior, of which we only observe the
inputs and the resulting outputs (Beliefs).

\begin{definition}{\bf Functional Block and Architecture --}\label{def:funblock}
	A functional block of an agent 
	takes a region of input-Beliefs and outputs a region of output-Beliefs. 
	A functional architecture is an interconnected system of functional blocks.
\end{definition}
The quality of a functional block or architecture can be expressed as a
relation between input and output belief, similarly to the quality of a channel
but inverting the flow (input$\rightarrow$output instead of
output$\rightarrow$input). In other words, we consider two properties:
how inputs are interpreted, and how outputs are produced.
One may, of course, argue that since there is a
transformation process in the functional block the quality of that
transformation process is what the theory should consider. This can
be argued not just for functional blocks (Behaviors) but also for Channels
(Assertions). \fix{mr}{The verification of the semantics of functional blocks and of the 
protocols executed over the channels will be considered at design level while
now we are still defining the specification}.
As we detail afterwards, the relations considered so
far revolves around the concept of integrity or availability, while the reminder of this section 
will be focused on a broader analysis of security properties and requirements;
which will also consider other security properties, such as availability and
confidentiality.  In order to define the quality of the internals of a functional block or channel, we first
need to relate the concept of Facts to engineering requirements.
